\input logicdocument
\title{Phil 210 - Quiz 3}

\heading
Quiz 3
Your Name
Introduction to Formal Logic
\endheading

Use a full or abbreviated truth table (your choice) to determine whether the following arguments are valid or invalid and state your answer.

\problems
\problem{1} (40 points.)
\argument
 A v B
 B v -A
++++++++++
 -A
\endargument
        \answer
        \truthtable
         A | B : A. v .B | B. v .-.A | -.A
        +++++++++++++++++++++++++++++++++++
           |   :  .   .  |  .   . .  |  . 
        \endtruthtable
        Valid/Invalid?
        \endanswer

\problem{2} (30 points.)
\argument
 A ^ B
 -[C ^ B]
++++++++++
 -C v -A
\endargument
        \answer
        \truthtable
         A | B | C : A. ^ .B | -.[.C. ^ .B.] | -.C. v .-.A
        +++++++++++++++++++++++++++++++++++++++++++++++++++
           |   |   :  .   .  |  .[. .   . .] |  . .   . . 
        \endtruthtable
        Valid/Invalid?
        \endanswer

\endproblems

Attempt to build countermodels for the following arguments to determine whether they're valid or invalid, given both the connectives predicates, then state your answer (and give the countermodel if possibe). You may again use whichever sort of truth table you want.

\problems
\problem{3} (20 points.)
\argument
 Shorter(alonzo,ruth) v Shorter(ruth,kurt)
 -[Shorter(alonzo,kurt) ^ Shorter(ruth,kurt)]
\argumentline
 -Shorter(alonzo,kurt)
\endargument
        \answer
        \truthtable
         S(a,r) | S(r,k) | S(a,k) : S(a,r). v .S(r,k) | -.[.S(a,k). ^ .S(r,k).] | -.S(a,k)
        +++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
                |        |        :       .   .       |  .[.      .   .      .] |  .   
        \endtruthtable

        \heightmodel
        
        \endheightmodel
        \OR
        No countermodel is possible, so it's valid, given the connectives and predicates.
        \endanswer

\problem{4} (10 points.)
\argument
 Shorter(ruth,kurt) v Shorter(ruth,alonzo)
 -[Shorter(alonzo,kurt) ^ Shorter(ruth,kurt)] v Shorter(ruth,alonzo)
\argumentline
 Shorter(ruth,kurt) v -Shorter(alonzo,kurt)
\endargument
        \answer\truthtableinteritemspace1.5pt
        \truthtable
         S(r,k) | S(r,a) | S(a,k) : S(r,k). v .S(r,a) | .-.[.S(a,k). ^ .S(r,k).]. v .S(r,a) | S(r,k). v .-.S(a,k)
        +++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
                |        |        :       .   .       | . .[.      .   .      .].   .       |       .   . .   
        \endtruthtable

        \heightmodel
        
        \endheightmodel
        \OR
        No countermodel is possible, so it's valid, given the connectives and predicates.
        \endanswer

\endproblems
\bye
