\input logicdocument
\title{Phil 210 - Quiz 4}

\heading
Quiz 4
Your Name
Introduction to Formal Logic
\endheading

Translate the following English sentences into the language of first-order logic.

\problems
\problem{1} (25 points.)
If Alonzo is a logician then so is Ruth.
        \answer
        $ $
        \endanswer

\problem{2} (20 points.)
If Ruth is not working, then she's happy.
        \answer
        $ $
        \endanswer

\problem{3} (15 points.)
Ruth is happy only if Alonzo is working.
        \answer
        $ $
        \endanswer

\problem{4} (10 points.)
Ruth is not happy if she and Alonzo are both working.
        \answer
        $ $
        \endanswer

\problem{5} (5 points.)
Alonzo isn't happy unless he's working or tired.
        \answer
        $ $
        \endanswer

\endproblems

Use a full or abbreviated truth table (your choice) to determine whether the following argument is valid or invalid and state your answer.

\problems
\problem{6} (15 points.)
\argument
 -A > C
 [A ^ B] > [C v -A]
\argumentline
 -B v A
\endargument
        \answer
        \truthtable
         A | B | C : -.A. > .C | [.A. ^ .B.]. > .[.C. v .-.A.] | -.B. v .A
        +++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
           |   |   :  . .   .  | [. .   . .].   .[. .   . . .] |  . .   .
        \endtruthtable
        Valid/Invalid?
        \endanswer

\endproblems

Attempt to build a countermodel for the following argument to determine whether it's valid or invalid, given both the connectives predicates. If it's invalid, give a countermodel. If it's valid, say so. You may again use whichever sort of truth table you want.

\problems
\problem{7} (10 points.)
\argument
 Shorter(alonzo,ruth) v Shorter(ruth,kurt)
 -[Shorter(alonzo,kurt) ^ Shorter(ruth,kurt)]
\argumentline
 -Shorter(alonzo,kurt)
\endargument
        \answer
        \truthtable
         S(a,r) | S(r,k) | S(a,k) : S(a,r). v .S(r,k) | -.[.S(a,k). ^ .S(r,k).] | -.S(a,k)
        +++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
                |        |        :       .   .       |  .[.      .   .      .] |  .
        \endtruthtable

        \heightmodel
         
        \endheightmodel
        \OR
        No countermodel is possible, so it's valid, given the connectives and predicates.
        \endanswer

\endproblems
\bye
